### 2022-03-15 ho-techniques/ho-techniques.tex
unif

\looseness=-1
The Boolean instantiation technique presented above requires delayed
clausification.
We assessed it in the best configuration from
%To assess it, we enabled it in the best configuration from
Fig.~\ref{fig:avatar-clause}, \relax{DCS}$-$\relax{LA}. With this change ($+$\relax{BI}),
Zipperposition proves \NumberOK{1700} TPTP problems and \NumberOK{456} SH
problems.
On TPTP, even though $+$\relax{BI} solves \NumberOK{3} problems less
than \relax{DCS}$-$LA, it is very useful: \NumberOK{41}
problems can be proved with $+$\relax{BI} but not with \relax{DCS}$-$\relax{LA}. 
Conversely, \NumberOK{44} problems are solved with \relax{DCS}$-$\relax{LA},
but not with $+$\relax{BI}, which suggests that Boolean instantiation can be 
explosive.
%
One of the problems Boolean instantiation helps solve is \texttt{NUM636\^{}2} (a
reencoding of \texttt{NUM636\^{}3}, which is discussed in Example \ref{hot:exa:num636}).
It conjectures that $\iforall x.\, \cst{s} \, x \ineq x$, where $x$ ranges over
Peano-style numbers specified by $\cst{z}$ and $\cst{s}$. The given axioms are
the induction principle $\forall p.\, p \, \cst{z} \,\iand\, \forall x. \, (p \,
x \iimplies p \, (\cst{s} \, x)) \iimplies \forall x. \, p\, x$, injectivity
$\forall x y. \, \cst{s}\,x \ieq \cst{s}\,y \iimplies x \ieq y$, and
distinctness $\forall x. \, \cst{s}\,x \ineq \cst{z}$. The conjecture is easily
proved if Boolean instantiation is enabled: Even though the conjecture literal
cannot be abstracted, instantiating $p$ with the term $\lambda x.\, \cst{s}
\, x \ineq x$ used in the encoding of the (nonclausified) conjecture leads to a proof in just
\NumberOK{22} given clause loop iterations. Zipperposition also finds a
proof using the \relax{DCI}$-$\relax{LA} configuration, but this requires
\NumberOK{294} iterations.

@@

In our previous work \cite{nbtv-2021-foboolsup}, we left this area of new
possibilities largely unexplored. We designed simple functions that selected
smallest, largest, innermost, or outermost terms, but they did not impact
performance much. Here, we propose alternatives.
%
Intuitively, a well-performing literal selection
function might succeed at taming the combinatorial explosion if the
selected literal can take part in few inferences
\cite{hrsv-16-selsel}. However, Boolean selection functions
introduce another factor to consider:\ the context in which the selected
subterm occurs. This suggests the following definition:

@@

>>>>

\looseness=-1
The Boolean instantiation technique presented above requires delayed
clausification.
We assessed it in the best configuration from
%To assess it, we enabled it in the best configuration from
Fig.~\ref{fig:avatar-clause}, \relax{DCS}$-$\relax{LA}. With this change ($+$\relax{BI}),
Zipperposition proves \NumberOK{1700} TPTP problems and \NumberOK{456} SH
problems.
On TPTP, even though $+$\relax{BI} solves \NumberOK{3} problems less
than \relax{DCS}$-$LA, it is very useful: \NumberOK{41}
problems can be proved with $+$\relax{BI} but not with \relax{DCS}$-$\relax{LA}. 
Conversely, \NumberOK{44} problems are solved with \relax{DCS}$-$\relax{LA},
but not with $+$\relax{BI}, which suggests that Boolean instantiation can be 
explosive.
%
One of the problems Boolean instantiation helps solve is \texttt{NUM636\^{}2} (a
reencoding of \texttt{NUM636\^{}3}, which is discussed in Example \ref{hot:exa:num636}).
It conjectures that $\iforall x.\, \cst{s} \, x \ineq x$, where $x$ ranges over
Peano-style numbers specified by $\cst{z}$ and $\cst{s}$. The given axioms are
the induction principle $\iforall p.\, p \, \cst{z} \,\iand\, \iforall x. \, (p \,
x \iimplies p \, (\cst{s} \, x)) \iimplies \iforall x. \, p\, x$, injectivity
$\iforall x y. \, \cst{s}\,x \ieq \cst{s}\,y \iimplies x \ieq y$, and
distinctness $\iforall x. \, \cst{s}\,x \ineq \cst{z}$. The conjecture is easily
proved if Boolean instantiation is enabled: Even though the conjecture literal
cannot be abstracted, instantiating $p$ with the term $\lambda x.\, \cst{s}
\, x \ineq x$ used in the encoding of the (nonclausified) conjecture leads to a proof in just
\NumberOK{22} given clause loop iterations. Zipperposition also finds a
proof using the \relax{DCI}$-$\relax{LA} configuration, but this requires
\NumberOK{294} iterations.

@@

In our previous work \cite{nbtv-2021-foboolsup}, we left this area of new
possibilities largely unexplored. We designed simple functions that selected
smallest, largest, innermost, or outermost terms, but they did not impact
performance much. A similar idea has been discussed in the context of \infname{Cases}(\infname{Simp}) rule
in Sect.~\ref{sect:bool:native}.  Here, we propose alternatives.
%
Intuitively, a well-performing literal selection
function might succeed at taming the combinatorial explosion if the
selected literal can take part in few inferences
\cite{hrsv-16-selsel}. However, Boolean selection functions
introduce another factor to consider:\ the context in which the selected
subterm occurs. This suggests the following definition:

@@

\section{Enumerating Infinitely Branching Inferences}
\label{sec:ho-tech:infinite-branching}

\looseness=-1
As an optimization and to simplify the code, Leo-III
\cite{as-18-phd} and Vampire 4.4 \cite{br-19-restricted-unif} (which uses
\confrep{}{\emph{restricted combinatory unification}, }a predecessor of combinatory
superposition) compute only a finite subset of the possible conclusions for
inferences that require enumerating a CSU. Not only is this a source of
incompleteness, but choosing the cardinality of the computed subset is a
difficult heuristic choice. Small sets can result in missing the necessary unifier, while large sets make the prover spend too long in
the unification procedure, generate useless clauses, and possibly get sidetracked into the wrong parts of the search space.

We propose a modification to the given clause procedure to seamlessly
interleave unifier computation and proof state exploration. Given a complete
unification procedure, which may yield infinite streams of unifiers, our
modification fairly enumerates all conclusions of inferences relying on
elements of a CSU. Under some reasonable assumptions, it behaves exactly like
the standard given clause procedure on purely first-order problems.
We also describe heuristics that help achieve a similar
performance as when using incomplete, terminating unification procedures
without sacrificing completeness.
\pagebreak[2]

Given that we cannot decide whether there exists a next CSU
element in a stream of unifiers, the request for the next conclusion might not
terminate,
effectively bringing the theorem prover to a halt. Our modified given clause procedure
expects the unification procedure to return a lazily computed stream
\cite[Sect.~4.2]{co-1999-funds}, where each element is either $\emptyset$ or
a singleton set containing a unifier. To avoid getting stuck waiting for a unifier
that may not exist, the unification procedure should return
$\emptyset$ after it performs some number of operations without finding a unifier.

The complete unification procedure described in Chapter \ref{ch:unif} returns such a stream. Other procedures such
as Huet's \cite{gh-75-unification} and Jensen and
Pietrzykowski's \cite{jp-76-unif} can easily be adapted to meet this
requirement. Based on the stream of unifiers interspersed with $\emptyset$, we
can construct a stream of inferences similarly interspersed with $\emptyset$.
Any finite prefixes of this stream can be computed in finite time.

To support such streams in the given clause procedure, we extend it to
represent the proof state not only by the active ($\mathcal{A}$) and passive ($\mathcal{P}$) clause
sets, but also by a priority queue $\mathcal{Q}$ containing the inference streams,
similar to the ``to do'' set $T$ present in the abstract Zipperposition loop of 
Waldmann et al.\  \cite[Sect.~4]{wtrb-20-sat-framework}.
Each stream is associated with a weight, and $\mathcal{Q}$ is sorted in order of
increasing weight\confrep{}{, a low weight corresponding to a high priority}.
When they introduced \lsup, Bentkamp et al.\
\cite{bbtvw-21-sup-lam} described an older version of this extension. Here
we present a newer version in more detail, including heuristics to postpone
unpromising streams. The pseudocode of the modified procedure is as follows:
\newcommand\ParamMode{\ensuremath{K_{\mathrm{fair}}}}
\newcommand\ParamMaxStreams{\ensuremath{K_{\mathrm{best}}}}
\newcommand\ParamRetry{\ensuremath{K_{\mathrm{retry}}}}
\newcommand{\assign}[2]{\State \ensuremath{\mathit{#1} \gets #2}}
\newcommand{\assignSameLine}[2]{\ensuremath{\mathit{#1} \gets #2}}
\algrenewcommand\algorithmicindent{1em}
\begin{algorithmic}[0]
    \Function{ExtractClause}{$Q$, $\mathit{stream}$}
      \assign{maybe\_clause}{\text{pop and compute the first element of } \mathit{stream} }
      \If{$\mathit{stream}$ is not empty}
        \State add $\mathit{stream}$ to $Q$ with an increased weight
      \EndIf
      \State \Return $\mathit{maybe\_clause}$
    \EndFunction

    \vspace{2\jot}

    \Function{HeuristicProbe}{$Q$}
      \assign{i}{0}
      \assign{collected\_clauses}{\emptyset}
      \While{$i < \ParamMaxStreams$ and $Q \not= \emptyset$}
        \assign{j}{0}
        \assign{maybe\_clause}{\emptyset}
        \While{$j < \ParamRetry$ and $Q \not= \emptyset$ and $\mathit{maybe\_clause} = \emptyset$}
          \assign{stream}{\text{pop the lowest-weight stream in } Q}
          \assign{maybe\_clause}{\textsc{ExtractClause}(Q, \mathit{stream})}
          \assign{j}{j+1}
        \EndWhile
        \assign{collected\_clauses}{\mathit{collected\_clauses} \mathrel\cup \mathit{maybe\_clause}}
        \assign{i}{i+1}
      \EndWhile
      \State \Return $\mathit{collected\_clauses}$
    \EndFunction

  \newpage
  \Function{FairProbe}{$Q$, $\mathit{num\_oldest}$}
    \assign{collected\_clauses}{\emptyset}
    \assign{oldest\_streams}{\text{pop } \mathit{num\_oldest} \text{ oldest streams from } Q}
    \For{$\mathit{stream}$ in $\mathit{oldest\_streams}$}
      \assign{collected\_clauses}{\mathit{collected\_clauses} \mathrel\cup \textsc{ExtractClause}(Q, \mathit{stream})}
    \EndFor
    \State \Return $\mathit{collected\_clauses}$
  \EndFunction

  \vspace{2\jot}

  \Function{ForceProbe}{$Q$}
    \assign{collected\_clauses}{\emptyset}
    \While {$Q \not= \emptyset$ and $\mathit{collected\_clauses} = \emptyset$}
      \assign{collected\_clauses}{\textsc{FairProbe}(Q, |Q|)}
    \EndWhile

    \If{$Q = \emptyset$ and $\mathit{collected\_clauses} = \emptyset$}
      \assign{status}{\textsf{Satisfiable}}
      % \Return (\textsf{Satisfiable}, $\mathit{collected\_clauses}$)
    \Else{}
      \assign{status}{\textsf{Unknown}}
      % \Return (\textsf{Unknown}, $\mathit{collected\_clauses}$)
    \EndIf

    \State \Return $(\mathit{status}, \mathit{collected\_clauses})$
  \EndFunction

  \vspace{2\jot}

  \Function{GivenClause}{$P$, $A$, $Q$}

  \assign{i}{0}
  \assign{status}{\textsf{Unknown}}
  \While{$\mathit{status} = \textsf{Unknown}$}
    \If{$P = \emptyset$}
      \assign{(status, \,forced\_clauses)}{\textsc{ForceProbe}(Q)}
      \assign{P}{P \mathrel\cup \mathit{forced\_clauses}}
    \Else
      \assign{given}{\text{pop a chosen clause from }P \text{ and simplify it}}
      \If{$\mathit{given}$ is the empty clause}
        \assign{status}{\textsf{Unsatisfiable}}
      \Else
        \assign{A}{A \mathrel\cup \{\mathit{given}\}}
        \For{$\mathit{stream}$ in streams of inferences between $\mathit{given}$ and $\mathit{other} \in A$}
          \If{$\mathit{stream}$ is not empty} \assign{P}{P \mathrel\cup \textsc{ExtractClause}($Q$, \mathit{stream})}
          \EndIf
        \EndFor
        \assign{i}{i+1}
        \If{$i \; \mathrm{mod} \; \ParamMode = 0$} \assign{P}{P \mathrel\cup \textsc{FairProbe}(Q, i/\ParamMode )}
        \Else{} \assign{P}{P \mathrel\cup \textsc{HeuristicProbe}(Q)}
        \EndIf
      \EndIf
    \EndIf
  \EndWhile

  \State \Return $\mathit{status}$

  \EndFunction
\end{algorithmic}
% \caption{Our modified given clause procedure}
% \label{fig:gc-pseudocode}
%
% \end{figure}
% \vspace{2.5\jot}

Entry point to the above pseudocode is the function \textsc{GivenClause}, called
with arguments $(\mathcal{P}, \mathcal{A}, \mathcal{Q})$, which are initialized
as usual: All input clauses are put into $\mathcal{P}$, and $\mathcal{A}$ and
$\mathcal{Q}$ are empty. In other words, the parameters $P, A$, and $Q$ intuitively
correspond to $\mathcal{P}, \mathcal{A}$, and $\mathcal{Q}$. Unlike in the
standard given clause procedure, inference results are represented as clause
streams. The first element is inserted into $P$, and the rest of the stream is
stored in $Q$ with some positive integer weight computed from the inference
rule.

\looseness=-1
To eventually consider inference conclusions from streams in $Q$ as given
clauses, we extract elements from, or \emph{probe}, streams and move any obtained
clauses to $P$. Analogously to the traditional pick--given ratio
\cite{ss-02-brainiac,mcw-1997-otter}, we use a parameter
\ParamMode{} (by default, $\ParamMode = 70$) to ensure fairness: Every \ParamMode{}th iteration,
\textsc{FairProbe} probes an increasing number of oldest streams, which achieves
dovetailing. In all other iterations, \textsc{HeuristicProbe} attempts to
extract up to \ParamMaxStreams{}~clauses from the most promising streams (by default,
$\ParamMaxStreams = 7$).
In each attempt, the most promising stream in $Q$ is chosen. If its first
element is $\emptyset$, the rest of the stream is inserted into $Q$ and a new stream is
chosen. This is repeated until either \ParamRetry{} occurrences of $\emptyset$ have  been
met (by default, $\ParamRetry = 20$) or the stream yields a singleton. Setting $\ParamRetry > 0$ increases
the chance that \textsc{HeuristicProbe} will return $\ParamMaxStreams$ clauses, as desired. Finally, if $P$ becomes empty, \textsc{ForceProbe}
searches relentlessly for a clause in $Q$, as a fallback.

\looseness=-1
The function \textsc{ExtractClause} extracts an element from a nonempty stream
not in $Q$ and inserts the remaining
stream into $Q$ with an increased weight, calculated as follows.
Let $n$ be the number of times the stream was chosen for
probing. If probing results in $\emptyset$, the stream's weight is increased by
$\max\,\{2{,}\; n-16\}$. If probing results in a clause $C$ whose penalty is
$p$, the stream's weight is increased by $p \cdot \max\,\{1{,}\; n-64\}$. The
penalty of a clause is a number assigned by Zipperposition based on
features such as the depth of its derivation and the rules used in it.
The constants $16$ and $64$ increase the chance that newer clause-producing streams are picked,
which is desirable because their first clauses are expected to be useful.

\looseness=-1
All three probing functions are invoked by
\textsc{GivenClause}, which contains the saturation loop. It differs
from the standard given clause procedure in three ways:
First, the proof state includes $Q$ in addition to $P$ and $A$. Second,
new inferences involving the given clause are added to $Q$ instead of being
performed immediately. Third, inferences in $Q$ are periodically performed
lazily to fill $P$.

\newcommand\infstream[1]{[#1]}

\begin{exa} 
  \begin{sloppypar}
  In this example we simplify the notation by writing positive predicate literals
  $\poslit{s}$ as $s$ and negative predicate literals $\neglit{t}$ as $\neg t$.
  Consider the unsatisfiable two-clause problem $\{ X \, (\cst{f} \,
  \cst{a}) \not\eq \cst{f} \, (X \, \cst{a}) \lor \cst{p} \, (X \, \cst{a}),\allowbreak
  \neg \cst{p} \, (\cst{f}^{100} \, \cst{a})  \}$ and a selection function which
  selects negative literals. 
  Let $P \mid A \mid Q$ denote
  the state of the given clause loop (i.e., the contents of the passive and active set
  and of the stream queue), and let $\infstream{ a_1, a_2, \ldots }$
  denote an infinite stream of elements.
  \end{sloppypar}

  The given clause loop begins in the state $X \, (\cst{f} \, \cst{a}) \not\eq
  \cst{f} \, (X \, \cst{a}) \lor \cst{p} \, (X \, \cst{a}), \neg \cst{p} \,
  (\cst{f}^{100} \, \cst{a}) \mid \emptyset \mid \emptyset$. If the clause $\neg
  \cst{p} \, (\cst{f}^{100} \, \cst{a})$ is chosen for processing, since $Q$ is empty
  and no inferences with the chosen clause are possible, the state becomes $X \,
  (\cst{f} \, \cst{a}) \not\eq \cst{f} \, (X \, \cst{a}) \lor \cst{p} \, (X \,
  \cst{a}) \mid \neg \cst{p} \, (\cst{f}^{100} \, \cst{a}) \mid \emptyset$. When
  the clause $X \, (\cst{f} \, \cst{a}) \not\eq \cst{f} \, (X \, \cst{a}) \lor
  \cst{p} \, (X \, \cst{a})$ is chosen, a new stream which enumerates results of
  equality resolution (on its first literal) is created. There are infinitely many
  conclusions of this inference, since there are infinitely many unifiers for the
  first literal of the form $\{ X \mapsto \lambda x. \, \cst{f}^i \, x \}$, for
  $i \geq 0$. Thus, the stream is $\infstream{ \{\cst{p} \, \cst{a}\}, \{\cst{p} \, (\cst{f}\,\cst{a})\}, \ldots }$,
  possibly with $\emptyset$s interspersed. With the standard given clause procedure,
  there would have been no way to represent this infinitary result.
  %The creation of the
  %inference result stream is the most striking difference between our
  %and standard given clause procedure.

  When the stream is created, its first element is popped and put into $P$. Then, based on the
  parameters that control inference stream probing, some number of clauses from
  the stream are computed and moved to $P$. After two iterations, the state might be
  $ \cst{p} \,
  \cst{a}, \cst{p} \, (\cst{f} \, \cst{a}), \allowbreak \cst{p} \, (\cst{f} \, (\cst{f} \, \cst{a}))   \mid X \,
  (\cst{f} \, \cst{a}) \not\eq \cst{f} \, (X \, \cst{a}) \lor \cst{p} \, (X \,
  \cst{a}), \neg \cst{p} \, (\cst{f}^{100} \, \cst{a}) \mid \infstream{ \{\cst{p} \, (\cst{f}^3\,\cst{a})\}, \ldots }$.

  In the next iterations, some clause of the form $\cst{p} \, (\cst{f}^{i} \,
  \cst{a})$, where $i < 100$, is chosen, but no inferences with it can be
  performed. Then, the stream created in the second iteration is probed, and its
  results fill the set $P$. Ultimately, the clause $\cst{p} \, (\cst{f}^{100} \,
  \cst{a})$ is chosen, at which point $\bot$ is quickly derived.
\end{exa}

\textsc{GivenClause} eagerly stores the first element of a new inference stream
in $P$ to imitate the standard given clause procedure. If the underlying
unification procedure behaves like the standard first-order unification
algorithm on higher-order logic's first-order fragment, our given clause
procedure coincides with the standard one. The unification procedure described in Chapter \ref{ch:unif}
terminates on the first-order and other fragments. To avoid computing
complicated unifiers eagerly, it immediately returns $\emptyset$ for a problem that does not
belong to one of the fragments that admit efficient unifier computation.

The design of our given clause procedure was guided by folklore knowledge about
higher-order theorem proving. First, in our experience most steps in
long higher-order proofs involve first-order literals. The unification
procedure and inference scheduling ensure that first-order inference
conclusions are put in the proof state as early as possible. Second, some
inference rules are expected to be largely useless. We initialize the stream
penalty differently for each rule, allowing old streams of more useful
inferences to be queried before newly added, but potentially less useful
streams. Finally, if we use a unification procedure that has aggressive
redundancy elimination, we will often find the necessary unifier within the
first few unifiers returned. Similarly, if a stream keeps returning
$\emptyset$, it is likely that it is blocked in a nonterminating computation
and should be ignored. Our heuristics to increase the stream penalties take
both observations into account.

\begin{sloppypar}

  The evaluation of our unification algorithm in Sect.~\ref{sec:unif:evaluation}
  shows that Zipperposition is the only competing
  higher-order prover that proves all Church numeral problems from the TPTP,
  never spending more than 5~s on a problem. On these hard
  unification problems, the stream system allows the prover to explore the proof
  state lazily.
\end{sloppypar}

Consider the TPTP problem \verb|NUM800^1|, which requires finding
a function $F$ such that $F \, \cst{c_1} \, \cst{c_2}
\ieq \cst{c_2} \iand F \, \cst{c_2} \, \cst{c_3} \ieq \cst{c_6}$, where
$\cst{c}_n$ abbreviates the Church numeral for~$n$, $\lambda s\, z. \>
s^n \, z$. To prove
\confrep{it}{the problem}, it suffices to take $F$ to be the multiplication operator
$\lambda x \, y \, s \, z. \> x \, (y \, s) \, z$.
However, this unifier is only one out of many available for each occurrence of
$F$.

% TODO: If I add a new benchmark set, make sure this sentence is fixed
\looseness=-1
For evaluation of our unification algorithm (using somewhat different
evaluation setup and older version of Zipperposition), we also compared a complete, nonterminating variant of the
unification procedure and a pragmatic, terminating variant. The
pragmatic variant was used directly---all the inference conclusions were put
immediately in $P$, bypassing $Q$. The complete variant, which relies on
possibly infinite streams and is much more prolific, proved only 15  problems
less than the most competitive pragmatic variant. Furthermore, it proved 19
problems not proved by the pragmatic variant.
%
This shows that our given clause procedure, with its heuristics, allows the
prover to defer exploring less promising branches of the unification and uses
the full power of a complete higher-order unifier search to solve unification
problems that cannot be proved by a restricted procedure.

\looseness=-1
The parameters \ParamMode{}, \ParamRetry{}, and \ParamMaxStreams{} can greatly
influence the behavior of the given clause procedure, even when the same
unification procedure is used. Figure~\ref{fig:streams}
presents the effects of these parameters on TPTP and SH.
Selecting a low number of best clauses seems to
perform well on both benchmark sets. However, on SH benchmarks, which require
overwhelmingly first-order unifiers, visiting older streams should be delayed
a lot.

As with Boolean selection functions, changing these three parameters causes
a substantial difference in the set of proved problems. For example, the
configuration that performs the worst on TPTP benchmarks proves \NumberOK{12}
problems that the configuration performing the best on TPTP cannot prove; moreover, there
are \NumberOK{29} TPTP problems that are proved by some set of parameters
other than $\ParamMode=\ParamMaxStreams=16, \ParamRetry=2$. On SH, these
effects are much weaker; most reasonable combinations
of parameters perform similarly.

Among the competing higher-order provers, only Satallax uses infinitely
branching calculus rules. It maintains a queue of ``commands'' that contain
instructions on how to create a successor state in the tableau. One
command describes infinite enumeration of all closed terms of a given function
type. Each execution of this command makes progress in the enumeration. Unlike
evaluation of streams representing elements of CSU, each command execution
is guaranteed to make progress in enumerating the next closed functional
term, so there is no need to ever return $\emptyset$.

\begin{figure}
\captionsetup[subfigure]{justification=centering}

\centering
\begin{subfigure}[b]{1\textwidth}
  \centering
  \begin{tabular}{@{}l@{\kern.5em}l@{\qquad}c@{\kern.75em}c@{\kern.75em}c@{}l@{}c@{\kern.75em}c@{\kern.75em}c@{}l@{}c@{\kern.75em}c@{\kern.75em}c@{}}\toprule
  &&&&&&& \ParamMode \\[.5\jot]
  & & & 2 & & \hbox{\qquad} & & 16 & & \hbox{\qquad} & & 128 & \\[.25\jot]
  \cline{3-5}\cline{7-9}\cline{11-13}
  \\[-1.5\jot]
  &&& \ParamRetry &&&& \ParamRetry &&&& \ParamRetry \\[.5\jot]
  %                                     2                        16                     256
  &                         & 2    & 16   & 128  & & 2         & 16   & 128  & & 2    & 16   & 128 \\\midrule
  & $2$                     & 1643 & 1645 & 1645 & & 1661      & 1661 & 1658 & & 1669 & 1664 & 1664 \\[0.5\jot]
  $\ParamMaxStreams$ & $16$ & 1647 & 1646 & 1609 & & {\bf1670} & 1654 & 1602 & & 1665 & 1659 & 1597 \\[0.5\jot]
  & $128$                   & 1646 & 1644 & 1583 & & 1661      & 1656 & 1577 & & 1665 & 1658 & 1576 \\ \bottomrule
  \end{tabular}
  \caption{TPTP benchmarks}
  \label{fig:streams-tptp}
\end{subfigure}
\par\bigskip
\begin{subfigure}[b]{1\textwidth}
  \centering
  \begin{tabular}{@{}l@{\kern.5em}l@{\qquad}c@{\kern.75em}c@{\kern.75em}c@{}l@{}c@{\kern.75em}c@{\kern.75em}c@{}l@{}c@{\kern.75em}c@{\kern.75em}c@{}}\toprule
  &&&&&&& \ParamMode \\[.5\jot]
  & & & 2 & & \hbox{\qquad} & & 16 & & \hbox{\qquad} & & 128 & \\[.25\jot]
  \cline{3-5}\cline{7-9}\cline{11-13}
  \\[-1.5\jot]
  &&& \ParamRetry &&&& \ParamRetry &&&& \ParamRetry \\[.5\jot]
  %                                          2                                               16                                      128
  &                         & 2            & 16            & 128          & & 2            & 16            & 128          & & 2                  & 16            & 128 \\\midrule
  & $2$                     & \colalign460 & \colalign455  & \colalign454 & & \colalign465 & \colalign463  & \colalign458 & & \colalign466       & \colalign461  & \colalign461 \\[0.5\jot]
  $\ParamMaxStreams$ & $16$ & \colalign458 & \colalign453  & \colalign445 & & \colalign464 & \colalign459  & \colalign441 & & \colalign{\bf468}  & \colalign459  & \colalign442 \\[0.5\jot]
  & $128$                   & \colalign456 & \colalign452  & \colalign430 & & \colalign465 & \colalign458  & \colalign428 & & \colalign{\bf468}  & \colalign459  & \colalign425 \\ \bottomrule
  \end{tabular}
  \caption{SH benchmarks}
  \label{fig:streams-sh}
\end{subfigure}
\caption{Impact of the stream enumeration parameter}
\label{fig:streams}
\end{figure}
